\section{Introduction}

\par
Welcome to \getTitle! \getTitleShort\, (for short) aims to provide a crunch-lite space adventure with a hard sci-fi background. Inspired by the works of authors like Robert Heinlein and Ursula K. Le Guin, \getTitleShort\, aims to give truly alien experiences without delving into space-fantasy or space-opera. We designed this system to keep things at least a little realistic, without bogging players down with excessive math or killyjoy-type limits on what you can do.

\par
Almost completely devoid of combat, \getTitleShort\, instead focuses on role-playing and acquiring the \skill s necessary to traverse the universe. \skillC s are easy to acquire and level up, but take a lot of work to perfect.

\par
That being said, there is the option for a \textit{lot} of math and calculation for technology and ships. If this is fun to you, crack out your slide rules (or go to \hyperlink{http://www.wolframalpha.com}{Wolfram Alpha}) and reckon your tragectory through the stars. If you'd like to keep the rocket science in the realm of story, that's also possible (though I did do a lot of research for all that).

\par
We hope you enjoy playing, but remember: if you don't like something, change it, and ignore any rules that ruin your fun. If "fun" to you is always following all the charts and calculating orbital transfers and insertations, then stick to that. If it means skipping by all that and just spending some fuel, then that's fine too. This is only a guide, after all. The most important part is the people at the table.

\par
\textit{-Alexander Lowry}