%Explaination on how skills and abilities work.

\section{\skillC s}

\par
\skillC s are specific areas of expertise that help you complete actions by giving a helpful bias to certain rolls. When you roll for an action, you can apply \textbf{one} of your \skill s to that roll, as long as the \gm\, agrees that your \skill\, is relevant to the action you're trying to do.

\par
Whenever you roll, you get one \xp . You can acquire a \skill\, by spending one \xp . You can also 'level up' \skill s. Leveling up \skill s means it biases your roll more strongly. A \skill\, can be upgraded twice, meaning that it can be as high as level 3. Each skill upgrade costs its level in \xp . You can do this at any time, during the game, before or after the session, or sitting at home in between sessions. The types of situations in which a \skill\, can be used are written underneath the \skill 's name. Also, the amount of the \modifier\, is listed.

\par
Check the \skill 's description since level 3 doesn't necessarily mean that it gives a +3 or -3 bias.

\par
Remember, the bias given by the \skill 's \modifier\, does not change based on your \both\, number. If you are heavily towards a \feelings\, direction, a \lasers\, skill \modifier\, is just as strong. Your overall odds of success on a \lasers\, roll is still low, but for certain \skill s it will still be higher than it would be without the \skill .

\par
Some \skill s have prerequisite \abilityP .

\subsection{\abilityPC}
\abilityPC\, are like skills, in that they cost \xp s but instead of aiding a roll, they allow you to do something you could not before. \abilityPC\, cost 5 \xp\, per level, across the board. \skillC s are about increasing the chances of success for things you already know how to do, but \abilityP\, are about doing new types of things. They may unlock new \skill s for you to acquire and upgrade.