%Contains a list of all skills an abilities
%Each list should be in alphabetical order.
%Generated based on data in 'skills.csv'
%And assembled via generate_skills.py

\section{List of \skillC s}
\hypertarget{skills}{}

\subsection{\feelingsC}
\hypertarget{skillsFeelings}{}

\paragraph{Aldrin}
\hypertarget{SkillAldrin}{}
+2/level on piloting, orbital rendezvous, and docking \textit{without instruments.}

\paragraph{Anthropologist}
\hypertarget{SkillAnthropologist}{}
+1/level understanding and learning a new culture.

\paragraph{Chameleon}
\hypertarget{SkillChameleon}{}
+1/level disguising as another species or culture.

\paragraph{Cook}
\hypertarget{SkillCook}{}
+2/level on making food.

\paragraph{Critter Wrangler}
\hypertarget{SkillCritterWrangler}{}
+1/level on creature-related shenanigans.

\paragraph{Diplomat}
\hypertarget{SkillDiplomat}{}
+1/level for persuading politicians, businesspeople, or leaders.

\paragraph{Envoy}
\hypertarget{SkillEnvoy}{}
+2/level on first contact messages and interactions.

\paragraph{Haggler}
\hypertarget{SkillHaggler}{}
+1/level while negotiating a deal with a salesperson or trader.

\paragraph{Linguist}
\hypertarget{SkillLinguist}{}
+1/level learning any new language.

\paragraph{Mathemagician}
\hypertarget{SkillMathemagician}{}
+1/level doing anything cool with math.

\paragraph{Trekker}
\hypertarget{SkillTrekker}{}
+1/level on figuring out where you're going on unfamiliar ground, with or without maps.

\subsection{\lasersC}
\hypertarget{skillsLasers}{}

\paragraph{Botanist}
\hypertarget{SkillBotanist}{}
-1/level on identifying and finding plants.

\paragraph{Cartographer}
\hypertarget{SkillCartographer}{}
-1/level on making and reading maps.

\paragraph{Engineer}
\hypertarget{SkillEngineer}{}
-1/level on operating and repairing machines.

\paragraph{Firefighter}
\hypertarget{SkillFirefighter}{}
-1/level on suppressing or preventing fires.

\paragraph{Historian}
\hypertarget{SkillHistorian}{}
-1/level on inferring or learning about local history.

\paragraph{Mechanic}
\hypertarget{SkillMechanic}{}
-2/level fixing devices you're familiar with.

\paragraph{Navigator}
\hypertarget{SkillNavigator}{}
-1/level on figuring out where you're going dirtside.

\paragraph{Pilot}
\hypertarget{SkillPilot}{}
-2/level on operating a flying vehicle. Tricks encouraged.

\paragraph{Radio Operator}
\hypertarget{SkillRadioOperator}{}
-2/level on operating radios.

\paragraph{Radio Scanner}
\hypertarget{SkillRadioScanner}{}
-1/level on identifying objects on radar and long-distance imaging.

\paragraph{Schematisizer}
\hypertarget{SkillSchematisizer}{}
-1/level on reading unfamiliar schematics.

\paragraph{Surgeon}
\hypertarget{SkillSurgeon}{}
-1/level for first aid, or large healing during resting times.

\paragraph{User Interfacer}
\hypertarget{SkillUserInterfacer}{}
-1/level on figuring out an unfamiliar or alien control scheme or device, or discerning something's function.

\section{List of \abilityPC}
\hypertarget{abilities}{}

\paragraph{Astrogator}
\hypertarget{SkillAstrogator}{}
Ability to navigate interstellar travel.

\paragraph{Dialectist}
\hypertarget{SkillDialectist}{}
Ability to learn a dialect of a language already known, in 7 days. At level 2, this is reduced to 3 days. At level 3, the \pc\, can figure out the jist of the dialect in about 1 conversation's time.

\paragraph{Experimenter}
\hypertarget{SkillExperimenter}{}
Ability to operate medically on alien physiology.

\paragraph{Star-Pilot}
\hypertarget{SkillStar-Pilot}{}
The \pc\, can pilot an interstellar vehicle.